\Huge{Machine Learning} \\ \LARGE Nature's Quest: Deep Learning Exploration of Global Plant Traits from Images and Geodata

### 2024-03-29 paper/paper.tex
fixes

\begin{figure}[!h]
    \centering
    \includegraphics[width=1\textwidth]{assets/lr_schedule_diffs.png}
    \caption{Comparison of different learning rate schedules}
    \label{fig:lr_schedules}
\end{figure}

@@

Another point of consideration we had was the training of the backbone. We wanted to test out whether there was any difference in $R^2$ whether we allowed the model to adapt the weights of the backbone or not. The results of this can be seen in \ref{fig:backbone_training} in both of these instances we see the model converging at around the 2nd epoch and hitting a plateau of $\approx -0.03 R^2$. This is likely due to the fact that the backbone requires little additional training to learn the features from the data and generalizes well to this task.

>>>>

\begin{figure}[!h]
    \centering
    \includegraphics[width=1\textwidth]{assets/lr_schedule_diffs.png}
    \caption{Comparison of different learning rate schedules ; (left) step-based ; (center) cosine annealing ; (right) exponential}
    \label{fig:lr_schedules}
\end{figure}

@@

Another point of consideration we had was the training of the backbone. We wanted to test out whether there was any difference in $R^2$ when we allowed the model to adapt the weights of the backbone or not. The results of this can be seen in \ref{fig:backbone_training} in both of these instances we see the model converging at around the 2nd epoch and hitting a plateau of $\approx -0.03 R^2$. This is likely due to the fact that the backbone requires little additional training to learn the features from the data and generalizes well to this task.
